---
title: "Statistical Consulting"
author: "Matteo Rossi"
date: "2023-09-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Statistical Consulting Project

## Importing initial packages

```{r}
library(dplyr)
```

## Importing the dataset

```{r}
library(readxl)
df_hrv = read_excel("DATA/ReviewPaper_hrv.xlsx")
df_meta = read_excel("DATA/ReviewPaper_meta.xlsx")
```

```{r}
colnames(df_hrv)
```


```{r}
df_hrv = df_hrv |> select(c("TITLE", "AUTHOR", "INCLUDED")) |>
  filter(!is.na(TITLE)) |> filter(INCLUDED == "yes") |>
  select(TITLE, AUTHOR) |> mutate(ID = 1:61, study_type = "hrv")

df_meta = df_meta |> select(c("TITLE", "AUTHOR", "INCLUDED")) |>
  filter(!is.na(TITLE)) |> filter(INCLUDED == "yes") |>
  select(TITLE, AUTHOR) |> mutate(ID = 1:34, study_type = "meta")
```

```{r}
df_tot = rbind(df_hrv, df_meta) |> select(ID, TITLE, AUTHOR, study_type)
df_tot
```
This is the full dataset. Now we will concentrate extracting from the different papers several effects size information regarding our problem:

## Extraction of Effects size

Importing the initial dataset provided by our client:

```{r}
df_data = read_excel("DATA/PaperCharacterizationTable_latest.xlsx", skip = 1) 
```

Data Manipulation for extracting the correct ID and Title to the following initial dataset:

```{r}
df_data = df_data[-c(4, 11, 20, 25, 26, 34, 36)]
colnames(df_data)
```


```{r}
df_done = df_meta[df_meta$AUTHOR %in% df_data$Authors,]
df_done
```

```{r}
df_data$ID = c(df_done$ID, rep(35, 3))

title = "The impact of metacognitive beliefs and anticipatory processing on state anxiety in high socially anxious individuals in a speech task"
df_data$Title = c(df_done$TITLE, rep(title, 3))
```


## Selecting the variables that we are interested

```{r}
colnames(df_data)
```

From this list of papers we have to extract those following information about. Now let's split the amount of work equally:

```{r}
df_meta_todo = df_meta[!df_meta$TITLE %in% df_data$Title, ]

set.seed(43)
indices = sample(30, 15)

df_meta_Matteo = df_meta_todo[indices,]
df_meta_Katie = df_meta_todo[-indices, ]
```


```{r}
write.csv(df_meta_Matteo, "Retrieving_data/Matteo_todo.csv", row.names = F)
write.csv(df_meta_Katie, "Retrieving_data/Katie_todo.csv", row.names = F)
```

```{r}
write.csv(df_data, "Retrieving_data/data_done.csv", row.names = F)
```




